---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# auseconhist

<!-- badges: start -->
[![R build status](https://github.com/MattCowgill/auseconhist/workflows/R-CMD-check/badge.svg)](https://github.com/MattCowgill/auseconhist/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

This R package provides convenient access to historical economic data from Australia, collated from various sources.

## Installation

Install from [GitHub](https://github.com/mattcowgill/auseconhist) with:

``` r
# install.packages("devtools")
devtools::install_github("MattCowgill/auseconhist")
```
## Usage

The seven appendix tables of [Butlin, Dixon and Lloyd 2014](https://doi.org/10.1017/CHO9781107445222.033) are available as `butlin_t1`,
`butlin_t2`, and so on. They are tibbles in 'wide' (ie. un-tidy) format, as in 
the source document.

Here's what table 1 looks like:
```{r}
library(auseconhist)

head(butlin_t1)
```

The variable names are short(ish) and use snake_case. For information about the
variables, see the dataset's documentation, with `?butlin_t1`, `?butlin_t2`, etc.

## Status

This package is in 'experimental' stage. Objects may change name. The package 
may be merged with another, such as [strayr](https://github.com/mattcowgill/strayr).
Please save local versions of any data you use in a script that you need to be 
reproducible. 

## Disclaimer

The data included in this package is reproduced from the source documents as noted
in the objects' help files.
